\chapter{Deliverable IV}
\textcolor{gray}{%
\begin{itemize}
    \item Write your answers on the questions in cases A, B, C and D covered during the lecture (see the lecture slides).
    \item Did your opinion on some of the ethical issues changed after you discussed the cases in the groups/classroom? Comment briefly on how if your answer to this question was positive.
    \item In the report write the names of all students participating at the group discussion.
\end{itemize}}

\section{Group Session}
\subsection{Participants}
\begin{multicols}{2}
    \begin{itemize}
        \item Claus Wiingreen, cwiing13 
        \item Jonas Madsen, jsma13
        \item Lars Nielsen, laniel13
        \item Louise Frederiksen, lfrede13 
        \item Mathias Michno, mmichn13
        \item Mathias Rasmussen, mvra13
        \item Rune Larsen, rala13
        \item Simon Pedersen, sape13
        \item Søren Larsen, slar12
        \item Thomas Nielsen, tpne13
    \end{itemize}
\end{multicols}
\subsection{Case A}
\begin{description}[style=unboxed]
    \item[What should Alyssa do?] \hfill\\
        Alyssa should not put Ben as co-author, since he has not done any of the work. She should seek funding, and it that is not possible, she should withdraw the paper from the conference.
    \item[How should Ben have handled the situation?] \hfill\\
        He should have commented on the drafts and addressed the problem from the start, rather than hiding it and being shy of conflict.
    \item[Is it reasonable to have expected Alyssa to have behaved any differently?] \hfill\\
        If we think ethically, no, she would not have behaved any differently. But if you look at it from a job perspective, she could have chosen differently because of the risk she takes, if she gets into a rift with the professor.
\end{description}
\subsection{Case B}
\begin{description}[style=unboxed]
    \item[Do you see any cases of irresponsible conduct?] \hfill\\
        It is irresponsible conduct of Anna to put Bob as co-author and of Bob to let her do it. It is also irresponsible conduct of Bob to put the paper in his PhD thesis, making it plagiarism.
    \item[If so, what would have been the appropriate responsible conduct?] \hfill\\
Anna should have gone to the professor with her draft and talked to him, what options she had, both including and excluding Bob.
    \item[What actions should be taken in the present situation, if any?] \hfill\\
It is not really possible to take actions, that could prove that they are guilty, without hitting innocent people.
\end{description}
\subsection{Case C}
\begin{description}[style=unboxed]
    \item[If the experiments are part of a series, are Paula and her students justified in not publishing them together?] \hfill\\
        If you decide to not publish them together, you have to make sure, that the papers do not become too simple. There is a danger of repetition if the experiments are split up and a danger of no new material.
    \item[If they decide to publish a single paper, how should the listing of authors be handled?] \hfill\\
Alphabetical order.
    \item[If a single paper is published, how can they emphasize to the review committees and funding agencies their various roles and the importance of the paper?] \hfill\\
This should not be necessary, but it can be done in the preface.
\end{description}
\subsection{Case D}
\begin{description}[style=unboxed]
    \item[How should the data from the two suspected runs be handled?] \hfill\\
Present and discuss why they are different.
    \item[Should the data be included in tests of the statistical significance and why?] \hfill\\
You could argue that they should not be included because of the fluctuations.
    \item[What other sources of information, in addition to their faculty adviser, can Deborah and Kathleen use to help decide?] \hfill\\
Contact laboratory workers and other professors.
\end{description}

\section{Plenary Session}
After discussing the cases in plenum I did not change opinion.
However I did become aware of other ways to present authors than alphabetical, e.g.\ divided into groups.

