\chapter{Deliverable V}
\textcolor{gray}{%
\begin{itemize}
    \item Write your answers on the questions in cases A, B and C covered during the lecture (see the lecture slides).
    \item Did your opinion on some of the ethical issues changed after you discussed the cases in the groups/classroom? Comment briefly on how if your answer to this question was positive.
    \item In the report write the names of all students participating at the group discussion.
\end{itemize}}

\section{Group Session}
\subsection{Participants}
\begin{multicols}{2}
    \begin{itemize}
        \item Christian Ovesen, covese13
        \item Henrik Thomsen, hthoms13
        \item Ida Thuesen, ithues12
        \item Kenneth Haunstrup, khch12
        \item Mathias Michno, mmichn13
        \item Simon Sillesen, ssille13
        \item Tristan Bendixen, tbendi13
        \item Zobair Qauomi, zqauom12
    \end{itemize}
\end{multicols}
\subsection{Case A}
\begin{description}[style=unboxed]
    \item[Do you see any cases of irresponsible conduct?] \hfill\\
        Yes, it is plagiarism to copy other people's work without giving credit. Yes, he listed a manuscript as a part of the thesis, but he hasn't included it in the thesis.
    \item[If so, what would have been the appropriate responsible conduct?] \hfill\\
        Give credit where credit is due and use quotation mark. Either he should not have included it or he should have written about it.
    \item[What actions should be taken in the present situation, if any?] \hfill\\
        As the plagiarism is not related to the main technical piece, and we assume that the motivating piece is not as essential, we decide: Reject the thesis, and then a committee should decide whether Mark should have a second attempt at his thesis. Inform the world leading university of this misconduct.
\end{description}
\subsection{Case B}
\begin{description}[style=unboxed]
    \item[Do you see any cases of irresponsible conduct?] \hfill\\
        The university and professor P does not know about the conversation between John and ComCom and John is not in a position to ``sell`` the idea to ComCom.
    \item[If so, what would have been the appropriate responsible conduct?] \hfill\\
        John should have mentioned the interest from ComCom to Professor P and to the university. He has the right to talk about the product, but he is not allowed to sell the idea.
    \item[What actions should be taken in the present situation, if any?] \hfill\\
        Cancel the deal he made with ComCom. He is not in a position to sell it and ComCom should know that. Or, tell the university and professor P about the idea and give ComCom the opportunity to counter the second contract.
\end{description}
\subsection{Case C}
\begin{description}[style=unboxed]
    \item[Does Ben have any way of receiving credit for his work?] \hfill\\
        If Ben can prove that his work is the original technique, he can potentially receive credit. If Dr. Freeman does not agree to give credit, he can, as an extreme alternative contact the conference about the experimental technique being unoriginal. If Ben cannot prove this, Ben cannot claim he was the original inventor.
    \item[Should he contact Dr. Freeman in an effort to have this work recognized?] \hfill\\
        Yes, Ben should contact Dr. Freeman personally first.
    \item[Is Ben's advisor mistaken in encouraging his students to be so open about their work?] \hfill\\
        No, Ben's advisor is not mistaken. The problem is not that Ben was too open, but instead that Dr. Freeman did not correctly cite Ben's work.
\end{description}

\section{Plenary Session}
My opinion did not change after discussing the cases in plenum.
