\chapter{Deliverable I}
\textcolor{gray}{%
\begin{itemize}
    \item Write one paragraph summary of the area where you do your current project.
    \item Find two suitable workshops and two suitable conferences where your current project work could be possibly published. The submission deadline for the conferences/workshops should be in 2016/2017. For each workshop/conference provide its full name, acronym, an URL to the home-page of the event and the submission deadline.
\end{itemize}}
\section{Project Summary} % (fold)
\label{sec:project_summary}
The area covered by our current project, Giraf, is the development of an Android device environment for autistic citizens. 
Some of the problems encountered during this development process, consists of the entangled nature of a multi-group project. 
Since Giraf is a multi-group project, with nine different groups of software students, a lot of the effort put into said project, focuses on the coordination and work distribution between groups. 
Moreover the Giraf project focuses on the deployment of a complex software product; this includes automated testing, continuous integration and usability testing among others.
% section project_summary (end)

\section{Suitable Options for External Exposure}
\subsection{Workshops}
\begin{description}
    \item[ICSE 2016] - The 38th International Conference on Software Engineering \\
    http://2016.icse.cs.txstate.edu/ \\
Deadline for submission: February 26 2016 \\
Note: ICSE, has a workshop along side the conference.
    \item[CHASE 2016] - The 9th International Workshop on Cooperative and Human Aspects of Software Engineering \\
http://www.chaseresearch.org/workshops/chase2016 \\
Deadline for submission: January 29 2016
\end{description}             
\subsection{Conferences} 
\begin{description}
    \item[ASSETS 2016] - The 18th International ACM SIGACCESS Conference on Computers and Accessibility \\
http://assets16.sigaccess.org/index.html \\
Deadline for submission: October 14 2016
    \item[MOBILESoft 2016] - IEEE/ACM International Conference on Mobile Software Engineering and Systems \\
http://mobilesoftconf.org/2016/ \\
Deadline for submission: January 25 2016
 
\end{description}
